%-------------------------
% Resume in Latex
% Template Author : Jake Gutierre
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\LARGE \scshape Zhang Jikun} \\ \vspace{1pt}
    \small +65 XXXX XXXX $|$ \href{mailto:x@x.com}{\underline{XXXXXXXXXXXXXXXX@gmail.com}} $|$ 
    \href{https://github.com/caando}{\underline{github.com/caando}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National University of Singapore}{August 2022 -- May 2025}
      {Bachelor of Computing, Computer Science (with Honours)}{}
    \resumeItemListStart
        \resumeItem{First Class Honours.}
        \resumeItem{Distinction in Algorithms \& Theory, Parallel Computing, Database Systems and Programming Languages focus areas. }
        \resumeItem{Integrating AI predictors in Sniper Multi-Core Simulator as Final Year Project. }
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Optiver} $|$ {Software Engineer Intern}}{May 2024 -- August 2024}
      \resumeItemListStart
        \resumeItem{C++ developer working on connectivity software.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Open Government Products} $|$ {Software Engineer Intern}}{May 2023 -- August 2023}
      \resumeItemListStart
        \resumeItem{Improved selection logic of GitHub tokens for API calls to double efficiency of rate limits and improve ease to monitor.}
        \resumeItem{Implemented features to Isomer such as preview images, last updated time and placeholder files.}
        \resumeItem{Drafted a plan to migrate Isomer's git service provider and over 800 hosted site repositories from GitHub to GitLab.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeProjectHeading
      {\textbf{Atom Assets Exchange} $|$ {Software Engineer Intern}}{January 2022 -- July 2022}
      \resumeItemListStart
        \resumeItem{Developed a native gateway client with Boost.ASIO that communicates execution data in TCP protocol to London Stock Exchange Group’s matching engine service.}
        \resumeItem{Developed a market data collection service with of exchanges over websockets and stores it in Apache Parquet format.}
        \resumeItem{Set up integration tests with GoogleTest framework for native gateway client and matching engine service.}
        \resumeItem{Contributed to the development of a market making strategy that quotes at 1 tick spread for high volume digital assets.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \footnotesize{\item{
     \textbf{High Performance}{: C, C++, Make, CMake, Boost, ASIO, Beast, GoogleTest} \\
     \textbf{Web}{: TypeScript, JavaScript, HTML, CSS, NodeJS, ExpressJS, ReactJS, JestJS, Axios, ChakraUI, Flask} \\
     \textbf{Database}{: SQL, MySQL, PostgreSQL, SQLite, Sequelize} \\
     \textbf{Data Modeling \& Analytics}{: Python, NumPy, Pandas, Matplotlib, Scikit-Learn, PyTorch, Tensorflow} \\
     \textbf{Tools \& Misc}{: Git, Docker, Amazon Web Services, \LaTeX} \\
    }}
 \end{itemize}

%-----------Achievements-----------
\section{Achievements}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ICPC Challenge} $|$ \emph{Algorithm/Heuristic Design Competition by Huawei}}{2023}
          \resumeItemListStart
            \resumeItem{Won Second Prize in Spring Online Challenge and achieved 26th place in onsite Challenge Championship with the problem Buffer Sharing(and Preallocation) for Multi-tenant Database Environment. }
            \resumeItem{Designed a caching algorithm that greatly outperforms common cache replacement policies such as Least Recently Used. }
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Ready Trader Go} $|$ \emph{Algorithmic Trading Competition by Optiver}}{March 2023}
          \resumeItemListStart
            \resumeItem{Reached top 16 by building an autotrader that reliably achieved profits and outperformed other autotraders.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Terminal} $|$ \emph{Strategic AI Programming Competition by Correlation One}}{August 2022}
          \resumeItemListStart
            \resumeItem{Champions in Summer Invitational for designing an AI in tower defense simulations that won all rounds in playoffs.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Competitive Programming Competitions} \emph{}}{2021 -- 2023}
          \resumeItemListStart
            \resumeItem{3rd in 2021 and 2nd in 2022 of Credit Suisse Global Coding Challenge, South-East Asia region.}
            \resumeItem{2nd in CodeIt Suisse 2022 Singapore Team Category.}
            \resumeItem{15th in Google Farewell round C 2023, 63rd in round D and 16th in round F of Google Kickstart.}
            % \resumeItem{319th in Meta Hacker Cup 2022, 125th in Quora Programming Challenge 2022 and Finalist in Shopee Code League.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

 %-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Minerva Chess Engine} $|$ \emph{C/C++, CMake, GoogleTest}}{May 2023 -- August 2023}
          \resumeItemListStart
            \resumeItem{Developed a chess engine that achieved approximately 2650 elo rating according to STS-rating test suites.}
            \resumeItem{Implemented chess programming techniques such as bitboards representation, bitwise move generation, quiescence and negamax search, transposition table with Zobrist hashing. Integrated StockFish NNUE for evaluating leaf nodes.}
            \resumeItem{Incorporated telegram bot front-end open for users to play against.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{SGExams Website} $|$ \emph{Javascript, ExpressJS, ReactJS, PostgreSQL, AWS}}{January 2020 -- August 2023}
          \resumeItemListStart
            \resumeItem{Served as team lead of a group of volunteering student developers in building the \href{https://www.exams.sg}{www.exams.sg} website.}
            \resumeItem{Notes repository with more than 20,000 registered users sharing and uploading their notes.}
            \resumeItem{Platform for the organisation to publicise their programmes and initiatives.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Exam Timetable Generator} $|$ \emph{Python, NumPy, Pandas, Matplotlib, Flask}}{May 2019 -- September 2019}
          \resumeItemListStart
            \resumeItem{Utilised genetic algorithm to assign examination invigilation duties for teachers, reducing manual administrative work.}
            \resumeItem{Deployed the functionalities on a web application with Python Flask.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
